#Baseball players Performance Exploration By Anu Achankunju
#========================================================

## About
This data set contains the  performance and physical aspects information of 1157 Baseball players like like height, weight and handedness of 1157 players. 

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using
# in your analysis in this code chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk.
# This prevents the code from displaying in the knitted HTML output.
# You should set echo=FALSE for all code chunks in your file.

library(ggplot2)
library(dplyr)
library(GGally)
library(scales)
library(memisc)
library(reshape)
library(gridExtra)
```



```{r echo=FALSE, warning=FALSE}
### Load and inspect data
setwd('C:\\Users\\320002667\\Box Sync\\NanoDegree\\M5_Make Effective Visualization\\MyProject\\data')
player_df<-read.csv('baseball_data.csv')
```

### What is the structure of your dataset?
Let's run some basic functions to examine the structure and schema of the data set.

```{r echo=TRUE, warning=FALSE}
dim(player_df)
names(player_df)
summary(player_df)
str(player_df)
```
 

Some initial observations are:

* There are 1577 observations of 7  variables.
* **Name** appears to be the unique identifier.
* **Home Runs** is a discrete variable. 
* All other variables except Handedness seem to be continuous numeric values.


##Exploratory Plots

###Home Runs Vs Height
```{r echo=FALSE, warning=FALSE}
 ggplot(aes(x=Height.cm. , y=Home.Runs), data = player_df)+
  geom_point()+
  xlab('Height')+
  ylab('Home Runs')+
  ggtitle('Home Runs Vs Height')+
  geom_smooth(color = 'red', linetype=1)
```

###Home Runs Vs Weight
```{r echo=FALSE, warning=FALSE}

 ggplot(aes(x=Weight.kg. , y=Home.Runs), data = player_df)+
  geom_point()+
  xlab('Weight')+
  ylab('Home Runs')+
  ggtitle('Home Runs Vs Weight')+
  geom_smooth(color = 'red', linetype=1)


```

###Home Runs Vs BMI Trend
```{r echo=FALSE, warning=FALSE}
ggplot(aes(x=BMI , y=Home.Runs), data = player_df)+
  xlab('BMI')+
  ylab('Home Runs')+
  ggtitle('Home Runs Vs BMI')+
  geom_point()+
  geom_smooth(color = 'red', linetype=1)

bmi <- player_df[,5]
homeruns <-player_df[,7]


min <- min(bmi);
max <- max(bmi);

# Creo i bin
Groups <- cut(x = bmi, breaks = seq(from = min, to = max, by = 2))
Groups <- data.matrix(Groups, rownames.force = NA)

# Raggruppo i dati nei bin
Bygroup = tapply(homeruns, Groups, mean)
Bygroup

# Faccio il plot dei bin
barplot(height = Bygroup, xlab = "bmi", ylab = "homeruns", main="Home Runs Vs Binned BMI")


```
```{r echo=FALSE, warning=FALSE}

```

```{r echo=FALSE, warning=FALSE}

```
